Spatial Coordination Of Stomatal Patterning Between Leaf Surfaces In Amphistomatous *Arabidopsis thaliana* Incurs No Photosynthetic Advantage

### 2023-09-26 ms/ms.Rmd
add new bibliography

---
# This template is largely functionally equivalent to that for elsevier
# The two fields that are not in the elsevier format are:
#      `corresponding_author` and `acknowledgements`
title: Spatial Coordination Of Stomatal Patterning Between Leaf Surfaces In Amphistomatous *Arabidopsis thaliana* Incurrs No Photosynthetic Advantage
#date: "`r Sys.Date()`"
author:
  - name: Jacob L. Watts
    email: jwatts@colgate.edu
    corresponding_author: yes # Footnote using corresponding_author
    affiliation: Colgate University
  - name: Graham Dow
    email: graham.dow@usys.ethz.ch
    affiliation: ETH
  - name: Thomas N. Buckley
    email: tnbuckley@ucdavis.edu
    affiliation: University of California Davis
    footnote: 1 # Footnote using reference
  - name: Christopher D. Muir
    email: cdmuir@hawaii.edu
    affiliation: University of Hawaii at Manoa
    footnote: 1 # Footnote using reference
address:
  - code: Colgate University
    address: 13 Oak Drive, Hamilton, NY 13346
  - code: University of Hawaii at Manoa
    address: 2500 Campus Rd, Honolulu, HI 96822
footnote:
  - code: 1
    text: "Equal contribution"
  - code: 2
    text: "Current email address: \\href{mailto:cat@example.com}{cat@example.com}"
abstract: |
  This is the abstract.

>>>>

---
# This template is largely functionally equivalent to that for elsevier
# The two fields that are not in the elsevier format are:
#      `corresponding_author` and `acknowledgements`
title: Spatial Coordination Of Stomatal Patterning Between Leaf Surfaces In Amphistomatous *Arabidopsis thaliana* Incurs No Photosynthetic Advantage
#date: "`r Sys.Date()`"
author:
  - name: Jacob L. Watts
    email: jwatts@colgate.edu
    corresponding_author: yes # Footnote using corresponding_author
    affiliation: Colgate University
  - name: Graham Dow
    email: graham.dow@usys.ethz.ch
    affiliation: ETH
  - name: Thomas N. Buckley
    email: tnbuckley@ucdavis.edu
    affiliation: University of California Davis
    footnote: 1 # Footnote using reference
  - name: Christopher D. Muir
    email: cdmuir@hawaii.edu
    affiliation: University of Hawaii at Manoa
    footnote: 1 # Footnote using reference
address:
  - code: Colgate University
    address: 13 Oak Drive, Hamilton, NY 13346
  - code: University of Hawaii at Manoa
    address: 2500 Campus Rd, Honolulu, HI 96822
footnote:
  - code: 1
    text: "Equal contribution"
  - code: 2
    text: "Current email address: \\href{mailto:cat@example.com}{cat@example.com}"
abstract: |
  This is the abstract.
